---
title: "Interactive charts with Highcharter"
author: 
date: "`r Sys.Date()`"
output:
  revealjs::revealjs_presentation:
    theme: solarized
    highlight: pygments
    center: true
---

# Champoupou champipi

## Maman Naka

## Words...
```{r packages, include = FALSE, warning = FALSE}
library(dplyr)
library(DT)
library(tidyr)
library(highcharter)
```

```{r words, echo=FALSE, message = FALSE, warning = FALSE}
data(diamonds, economics_long, mpg, package = "ggplot2")
library(dplyr)
DT::datatable(mpg[1:10,1:5])
``` 

## Papa Joel
```{r data, echo=FALSE, message = FALSE, warning = FALSE}
library(highcharter)
mpgman2 <- mpg %>% 
  count(class, year)
# %>% 
#   glimpse()
dtemp <- structure(list(month = c("Jan", "Feb", "Mar", "Apr", 
                                  "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                        tokyo = c(7, 6.9, 9.5, 14.5, 18.2, 21.5, 
                                  25.2, 26.5, 23.3, 18.3, 13.9, 9.6), 
                        new_york = c(-0.2, 0.8, 5.7, 11.3, 17, 22, 
                                     24.8, 24.1, 20.1, 14.1, 8.6, 2.5), 
                        berlin = c(-0.9, 0.6, 3.5, 8.4, 13.5, 17, 
                                   18.6, 17.9, 14.3, 9, 3.9, 1), 
                        london = c(3.9, 4.2, 5.7, 8.5, 11.9, 15.2, 
                                   17, 16.6, 14.2, 10.3, 6.6, 4.8)), 
                   .Names = c("month", "tokyo", "new_york", "berlin", "london"), 
                   row.names = c(NA, 12L), 
                   class = c("tbl_df", "tbl", "data.frame"))
```

```{r picture, echo=FALSE, message = FALSE, warning = FALSE}    
#hchart(mpg, "scatter", hcaes(x = displ, y = hwy, group = class))
``` 

# Je vous aime

## Je m'appelle Ryan Eduwodji Kodjo

Highcharts is a charting library:

* written in pure JavaScript
* offering an easy way of adding interactive charts to web site/application
* supports line, spline, area, areaspline, column, bar, pie, scatter, angular gauges, arearange, areasplinerange, columnrange, bubble, box plot, error bars, funnel, waterfall and polar chart types.

https://www.highcharts.com/

Warning: a license is needed to use Highcharts

# Bisous

## Bisous

Highcharter is a R wrapper for Highcharts javascript libray and its modules.  
It allows to reproduce all Highcharts interactive charts with R.

Warning: 'Highcharts (www.highcharts.com) is a Highsoft software product which is not free for commercial and Governmental use'

## Moua